
\prefacesection{Publications}
%\begin{singlespace}
\begin{enumerate}
\item \textit{User Modeling for Interactive Evolutionary Computation
Applications Using Fuzzy Logic. JC Romero, Mario Garc\'ia-Vald\'ez.
 Recent Advances on Hybrid Intelligent Systems. Springer Berlin Heidelberg. (2013)}
\item \textit{ EvoSpace-i: a framework for interactive evolutionary algorithms.
Mario Garc\'ia-Vald\'ez, 	Juan J. Merelo, 	Leonardo Trujillo, 	Francisco
Fernández-de-Vega Jos\'e C. Romero, 	Alejandra Mancilla. GECCO '13 Companion
Proceedings of the 15th annual conference  companion on Genetic and evolutionary
computation. Amsterdam, The Netherlands. (2013).}
\item \textit{Using a Graph Based Database to Support Collaborative Interactive
Evolutionary Systems.  JC Romero, Mario Garc\'ia-Vald\'ez. Recent Advances on
Hybrid Approaches for Designing Intelligent Systems. Springer International
Publishing Switzerland. Volume 547 of the series Studies in Computational
Intelligence pp 581-591. Switzerland. (2014).}
\item \textit{A Fitness Estimation Strategy for Web Based Interactive Evolutionary
Applications Considering User Preferences and Activities Using Fuzzy Logic. J.C.
Romero, Mario Garc\'ia-Vald\'ez. Design of Intelligent Systems Based on Fuzzy
Logic, Neural Networks and Nature-Inspired Optimization. Springer International
Publishing Switzerland. Volume 601 of the series Studies in Computational
Intelligence pp 507-516. (2015).}
\item \textit{Modeling Human Interactions in
Collaborative Interactive Evolutionary Computation.  Mario Garc\'ia-Vald\'ez,
Christian Romero, Juan. J. Merelo, Alejandra Mancilla.  In Proceedings of the Genetic and Evolutionary Computation
Conference 2017, Berlin, Germany, July 15-19, 2017 (GECCO ’17).}
\item \textit{Exploiting the Social Graph: Increasing Engagement in a Collaborative Interactive Evolution Applications.
Mario Garc\'ia-Vald\'ez,
Christian Romero, Juan. J. Merelo, Alejandra Mancilla.  In Proceedings of IEEE Congress on Evolutionary Computation 2017
Donostia - San Sebastián, Spain
June 5-8, 2017.}
\end{enumerate}
%\end{singlespace}
